Interval Probability for Fuzzy Quantum Theories

### 2016-05-14 prob.tex
prob.tex Updated summation notation and other thing according to meeting

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}

@@

The conventional definition of a probability
space~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
builds upon the real numbers. In more detail, a probability space
consists of a \emph{sample space} $\Omega$, a space of
\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
mapping events in $\events$ to the real interval $[0,1]$. In this
paper, we will only consider \emph{finite} sets of events: we
therefore restrict our attention to non-empty finite sets $\Omega$ as
the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
set of events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_i$ of pairwise disjoint events, 
  $\pmeas(\bigcup_i E_i) = \sum_i \pmeas(E_i)$.
\end{itemize}

@@

%%%%%
\subsection{Calculating Probabilities: Buffon's Needle Problem}

@@

As motivated above, an event $E_1$ may have an interval of probability
$[l_1,r_1]$. Assume that another disjoint event $E_2$ has interval
probability $[l_2,r_2]$, what is the interval probability of the event
$E_1 \cup E_2$. The answer is somewhat subtle: although it is possible
to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
probability, one can do find a much tighter interval if information
\emph{against} the event (i.e., information about the complement
event) is also taken into consideration. Formally, for a general event
$E$ with probability $[l,r]$, the strength of evidence that
contradicts $E$ is evidence supporting the complement of $E$. The
complement of $E$ must therefore have probability
$\left[1-r,1-l\right]$ which we abbreviate $1-\left[l,r\right]$. Given
a collection of intervals $\mathscr{I}$, an
$\mathscr{I}$--interval-valued probability measure is a function
$\pmeas : \events \rightarrow \mathscr{I}$ such that:
\begin{itemize}
\item $\pmeas(\emptyset)=[0,0]$, 
\item $\pmeas(\Omega)=[1,1]$, 
\item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$,
  and 
\item for a collection $E_{i}$ of pairwise disjoint events, we have
  $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$
  where the summation on the right is the summation of intervals that
  sums the endpoints.
\end{itemize}

@@

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

Notice that the preceding definition exhaust all possible projection operators.
Because every linear subspace~$S$ has an orthonormal basis~$\{\ket{\psi_j}\}$,
the projection onto $S$ can always expressed as $\sum_j\proj{\psi_j}$.
As operators, we can also multiply projections together.

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections as in
  definition~\ref{def:Projection};
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_i$, we have
  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
\end{itemize}
\qed\end{definition}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}

@@

The conventional definition of a probability
space~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
builds upon the real numbers. In more detail, a probability space
consists of a \emph{sample space} $\Omega$, a space of
\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
mapping events in $\events$ to the real interval $[0,1]$. In this
paper, we will only consider \emph{finite} sets of events: we
therefore restrict our attention to non-empty finite sets $\Omega$ as
the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
set of events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
where $a_{1}\tensor*[_{\mathbb{R}}]{+}{}a_{2}$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
explicitly specify $a_{i}\in\mathbb{R}$. We may drop the preposing
$\mathbb{R}$ when there is no confusion. 
\end{itemize}

@@

%%%%%
\subsection{Measuring Probabilities: Buffon's Needle Problem}

@@

As motivated above, an event $E_1$ may have an interval of probability
$[l_1,r_1]$. Assume that another disjoint event $E_2$ has interval
probability $[l_2,r_2]$, what is the interval probability of the event
$E_1 \cup E_2$. The answer is somewhat subtle: although it is possible
to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
probability, one can do find a much tighter interval if information
\emph{against} the event (i.e., information about the complement
event) is also taken into consideration. Formally, for a general event
$E$ with probability $[l,r]$, the strength of evidence that
contradicts $E$ is evidence supporting the complement of $E$. The
complement of $E$ must therefore have probability
$\left[1-r,1-l\right]$ which we abbreviate $1-\left[l,r\right]$. Given
a collection of intervals $\mathscr{I}$, an
$\mathscr{I}$--interval-valued probability measure is a function
$\pmeas : \events \rightarrow \mathscr{I}$ such that:
\begin{itemize}
\item $\pmeas(\emptyset)=[0,0]$, 
\item $\pmeas(\Omega)=[1,1]$, 
\item $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$,
  and 
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{I}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
where $\tensor*[_{I}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
We may drop the preposing $I$ when summands are clear intervals. 
\end{itemize}

@@

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any pure state~$\ket{\psi}$, $P=\proj{\psi}$ is a projection. 
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

Notice that the preceding definition exhausts all possible projection operators.
Because every linear subspace~$S$ has an orthonormal basis~$\{\ket{\psi_j}\}$,
the projection onto $S$ can always expressed as $\sum_j\proj{\psi_j}$.
As operators, we can also multiply projections together.

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections as in
  definition~\ref{def:Projection};
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_{i}$, we have $\mu\left(\tensor*[_{O}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$,
where $\tensor*[_{O}]{\sum}{_{i}}$ specifies that we add operators,
and the preposing $O$ may be dropped when summands are clearly operators.
\end{itemize}
\qed\end{definition}
